Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-31 manuscript.Rmd
Fix typo
Fix figures

The corpus of tweets used included `r tweet_stats$total_tweets` English-language
Syrian tweets occurring between March 31--June 15, 2012. Using the Twitter
streaming API, servers at the University of Texas at Austin collected the
tweets. The servers were run on a stable (LTS) version of Ubuntu Linus (v.
10.04) and were connected directly to the high-bandwidth UT network maintained
by IT services.

@@

For positive events, we see a similar early peak in RR, but the later
above-chance values did not match up temporally with that of the all-events time
series (FIX Figure 10). This suggests that the early stretch of above-chance RR
may have been captured in the RR of the all-events analysis, whereas the shorter
stretches were overshadowed by the coupling with negative events. The early
period of above-chance DET in the positive-event analysis aligned with the early
period of above-chance RR, whereas the later stretch of significant DET values
aligns temporally with that of the all-events analysis. It is possible that the
later stretch reflected the decrease in the number of positive events happening
(FIX see Fig. 4), while the relative sparsity of positive events led to an
increase in coupling, with denizens rallying around dwindling bits of hope as
time went on.

>>>>

The corpus of tweets used included `r tweet_stats$total_tweets` English-language
Syrian tweets occurring between March 31--June 15, 2012. Using the Twitter
streaming API, servers at the University of Texas at Austin collected the
tweets. The servers were run on a stable (LTS) version of Ubuntu Linux (v.
10.04) and were connected directly to the high-bandwidth UT network maintained
by IT services.

@@

For positive events, we see a similar early peak in RR, but the later
above-chance values did not match up temporally with that of the all-events time
series (Figure \@ref(fig:plot-wcrqa-targ-all)). This suggests that the early
stretch of above-chance RR may have been captured in the RR of the all-events
analysis, whereas the shorter stretches were overshadowed by the coupling with
negative events. The early period of above-chance DET in the positive-event
analysis aligned with the early period of above-chance RR, whereas the later
stretch of significant DET values aligns temporally with that of the all-events
analysis. It is possible that the later stretch reflected the decrease in the
number of positive events happening (see Figure \@ref(fig:raw-event-ts-target)),
while the relative sparsity of positive events led to an increase in coupling,
with denizens rallying around dwindling bits of hope as time went on.
